Combined annotation exploration for SCPCP000006

### 2024-11-14 analyses/cell-type-wilms-tumor-06/notebook/04_annotation_Across_Samples_exploration.Rmd

```{r path_to_query}
sample_metadata_file <- file.path(repository_base, "data", "current", "SCPCP000006", "single_cell_metadata.tsv")

metadata <- read.table(sample_metadata_file, sep = "\t", header = TRUE) |>
  dplyr::filter(seq_unit != "spot")

# Create a data frames of all annotations
cell_type_df <- metadata$scpca_sample_id |>
  purrr::map(
    # For each sample_id, do the following:
    \(sample_id) {
      input_file <- file.path(
        result_dir,
        sample_id,
        glue::glue("02b-fetal_kidney_label-transfer_{sample_id}.Rds")
      )

>>>>

```{r path_to_query}
sample_metadata_file <- file.path(repository_base, "data", "current", "SCPCP000006", "single_cell_metadata.tsv")
metadata <- read_tsv(sample_metadata_file)

sample_ids <- metadata |>
  dplyr::filter(seq_unit != "spot") |>
  dplyr::pull(scpca_sample_id) |>
  unique()

# Create a data frames of all annotations
cell_type_df <- sample_ids |>
  purrr::map(
    # For each sample_id, do the following:
    \(sample_id) {
      input_file <- file.path(
        result_dir,
        sample_id,
        glue::glue("02b-fetal_kidney_label-transfer_{sample_id}.Rds")
      )

### 2024-11-14 analyses/cell-type-wilms-tumor-06/notebook/07_combined_annotation_across_samples_exploration.Rmd

- the proportion of estimated CNV per chromosome, {i} in 1 to 22 `proportion_cnv_chr{i}`

- the `counts`of [markers genes](https://github.com/AlexsLemonade/OpenScPCA-analysis/tree/main/analyses/cell-type-wilms-tumor-06#the-table-celltype_metadatacsv-contains-the-following-column-and-information)

```{r path_to_query}
sample_metadata_file <- file.path(repository_base, "data", "current", "SCPCP000006", "single_cell_metadata.tsv")

metadata <- read.table(sample_metadata_file, sep = "\t", header = TRUE)
sample_ids <- metadata |>
  dplyr::filter(seq_unit != "spot") |>
  dplyr::pull(scpca_sample_id) |>
  unique()

>>>>

- the proportion of estimated CNV per chromosome, `{i}` in 1 to 22 `proportion_cnv_chr{i}`

- the `counts` of [markers genes](https://github.com/AlexsLemonade/OpenScPCA-analysis/tree/main/analyses/cell-type-wilms-tumor-06#the-table-celltype_metadatacsv-contains-the-following-column-and-information)

```{r path_to_query}
sample_metadata_file <- file.path(repository_base, "data", "current", "SCPCP000006", "single_cell_metadata.tsv")
metadata <- read.table(sample_metadata_file, sep = "\t", header = TRUE)

sample_ids <- metadata |>
  dplyr::filter(seq_unit != "spot") |>
  dplyr::pull(scpca_sample_id) |>
  unique()
